A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-11-03 controlled_study/controlled_study.tex
more spell checks
adds ethics certificate

%\documentclass[conference]{IEEEtran}

%\ifCLASSINFOpdf
  %\usepackage{listings}
  %\usepackage[pdftex]{graphicx}
  %\usepackage{url}
  %\usepackage{subcaption}
  %\usepackage{tikz,pgfplots,pgfplotstable}
  %\usepackage{mathtools}
  %\usepgfplotslibrary{statistics}
  %\usepackage{courier}
%\else
%\fi

%\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\def\ps@IEEEtitlepagestyle{%
  %\def\@oddfoot{\mycopyrightnotice}%
  %\def\@evenfoot{}%
%}
%\def\mycopyrightnotice{%
  %{\footnotesize 978-1-5386-0443-4/17/\$31.00 ©2017 IEEE\hfill}% <--- Change here
  %\gdef\mycopyrightnotice{}% just in case
%}
%\begin{document}
%\title{A Study of the Effectiveness of Usage Examples in REST API Documentation}
\chapter{A Study of the Effectiveness of Usage Examples in REST API Documentation}
\label{chapter:controlled_study}

 %\author{\IEEEauthorblockN{S M Sohan, Frank Maurer\IEEEauthorrefmark{1}}
 %\IEEEauthorblockA{\IEEEauthorrefmark{1}
 %Dept. of Computer Science\\
 %University of Calgary\\
 %Canada\\
 %\{smsohan, frank.maurer\}@ucalgary.ca}
 %\and
 %\IEEEauthorblockN{Craig Anslow}
 %\IEEEauthorblockA{School of Eng. and Computer Science\\
 %Victoria University of Wellington\\
 %New Zealand\\
 %craig@ecs.vuw.ac.nz}
 %\and
 %\IEEEauthorblockN{Martin P. Robillard}
 %\IEEEauthorblockA{
 %School of Computer Science\\
 %McGill University\\
 %Canada\\
 %martin@cs.mcgill.ca}
 %}

%\maketitle

@@

%\begin{IEEEkeywords}
%API; REST; Documentation; Usage Examples; Empirical Study; Controlled Study; Productivity;

%\end{IEEEkeywords}

%\IEEEpeerreviewmaketitle

@@

To answer the aforementioned research question, the study has the following requirements:

\begin{itemize}
  \item \textbf{R1. Representative API.} We had to choose an existing REST API that is currently used by API client developers. Selecting a mature REST API for this study reduces the possibility that the obstacles we observe in the study are the results of insignificant accidental problems symptomatic of an immature technology. We selected a familiar domain so that participants are able to relate to the API features without requiring upfront training. In addition to selecting the API, we had to select tasks that are related to the core features provided by the API to represent a common usage area of the API.
  \item \textbf{R2. Open source.} To be able to understand the impact of usage examples, we needed to select an open-source API where we can add new examples to the documentation for performing this study.
  \item \textbf{R3. Time bound.} We applied a maximum time constraint for each participant to measure the rate of success within a limited time frame. As a result, the study needs to be setup such that participants are able to focus on performing the tasks minimizing any overhead.
  \item \textbf{R4. Participant Selection.} Developers with prior experience on REST APIs need to be recruited as study participants to perform the study within a limited amount of time and in a realistic setup. Furthermore, to reduce a learning bias, only participants with no prior experince of using the WordPress REST API V2 are accepted for this study.
\end{itemize}

>>>>

\chapter{\texorpdfstring{A Study of the Effectiveness of Usage Examples in REST API Documentation \protect\footnote{S. Sohan, C. Anslow, F. Maurer, and M. Robillard, ``A study of the effectiveness of usage examples in REST API documentation,'' in to appear in Proc. of IEEE Symposium on Visual Languages and Human-Centric Computing, 2017.}}{A Study of the Effectiveness of Usage Examples in REST API Documentation}}
\label{chapter:controlled_study}

@@

@@

To answer the aforementioned research question, the study has the following requirements (Ethics Certificate in Appendix~\ref{ethics}):

\begin{itemize}
  \item \textbf{R1. Representative API.} We had to choose an existing REST API that is currently used by API client developers. Selecting a mature REST API for this study reduces the possibility that the obstacles we observe in the study are the results of insignificant accidental problems symptomatic of an immature technology. We selected a familiar domain so that participants are able to relate to the API features without requiring upfront training. In addition to selecting the API, we had to select tasks that are related to the core features provided by the API to represent a common usage area of the API.
  \item \textbf{R2. Open source.} To be able to understand the impact of usage examples, we needed to select an open-source API where we can add new examples to the documentation for performing this study.
  \item \textbf{R3. Time bound.} We applied a maximum time constraint for each participant to measure the rate of success within a limited time frame. As a result, the study needs to be setup such that participants are able to focus on performing the tasks minimizing any overhead.
  \item \textbf{R4. Participant Selection.} Developers with prior experience on REST APIs need to be recruited as study participants to perform the study within a limited amount of time and in a realistic setup. Furthermore, to reduce a learning bias, only participants with no prior experience of using the WordPress REST API V2 are accepted for this study.
\end{itemize}
